Untitled

### 2022-07-06 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
some edits on sup mat

Here we describe the different traits of the database used in this study to explore the reproductive spectrum of trait variation and plant-pollinator associations. Note that all species have references or links providing the original source of the information.

@@

-	Breeding system: The different plant species were classified in hermaphrodite, dioecious and monoecious species. Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.

-	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data. The qualitative data was divided in four main categories, high selfers, medium selfers, low selfers and none which was for the species that were unable to self-pollinate. In addition, quantitative data was also divided into these four categories with the following criteria: from 0% to lower than 1% ‘none’, from 1% to 25% ‘low’, from 26% to 75% ‘medium’ and from 76% to 100%  ‘high’. Because quantitative selfing had a high percentage of missing values (68%), we were able to solve this by converting these four categories to representative percentages of each category 0%, 13%, 50.5% and 88%. This reduced the percentage of missing values for this quantitative trait from 68% to 35% and allowed the imputation of this variable.

@@

-	Flower symmetry: We also recorded if the flowers were bilaterally symmetrical “zygomorphic” or were radially symmetrical “actinomorphic”.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig. S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation. Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3. For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)"}

>>>>

Here we describe the different individual traits that have been included in the database:

@@

-	Breeding system: All species were classified in hermaphrodite, dioecious and monoecious species. Intermediate breeding systems or more complex ones were also annotated but all the species were divided into these three main categories for simplicity of the analysis.

-	Selfing level: We recorded the selfing level of the different species with both quantitative and qualitative data. The qualitative data was divided in four main categories, high selfers (76% to 100% of selfing), medium selfers (26% to 75%), low selfers (1% to 25%) and none (0%) which was for the species that were unable to self-pollinate. The quantitative column of selfing had a high percentage of missing values (68%) but we were able to solve this by converting the four categories from the qualitative column to numerical. For this, we considered the mean value of the different categories, that is the categories of ‘none’, ‘low’, ‘medium’ and ‘high’ represented 0%, 13%, 50.5% and 88% of selfing, respectively. This reduced the percentage of missing of this column from 68% to 35% and allowed the imputation of this variable.

@@

-	Flower symmetry: Depending on the possible number of identical divisions of a flower, plant species were classified into zygomorphic (bilaterally symmetrical with only two identical parts) and actinomorphic (radially symmetrical with more than three identical parts).

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig. S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation. Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3. For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)."}
